Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2021-03-02 journal paper/content/related_work.tex
Removed some old coloring in a few more places.

A long line of work from electrical engineering and computer science, starting from
\citet{MultiPlayerMAB-Poor08,MultiPlayerMAB-Liu10}, focuses on competition for resources, not competition for consumers. Specifically, this literature targets an application to \emph{cognitive radios}, where multiple radios transmit simultaneously in a shared medium and compete for bandwidth. Each radio chooses channels over time using a multi-armed bandit algorithm. This work studies a repeated game between bandit algorithms, and focuses on designing algorithms which work well in this game\gadelete{, under various assumptions on communication, synchronization and collisions}.

>>>>

A long line of work from electrical engineering and computer science, starting from
\citet{MultiPlayerMAB-Poor08,MultiPlayerMAB-Liu10}, focuses on competition for resources, not competition for consumers. Specifically, this literature targets an application to \emph{cognitive radios}, where multiple radios transmit simultaneously in a shared medium and compete for bandwidth. Each radio chooses channels over time using a multi-armed bandit algorithm. This work studies a repeated game between bandit algorithms, and focuses on designing algorithms which work well in this game.
%\gadelete{, under various assumptions on communication, synchronization and collisions}.

### 2021-03-02 journal paper/content/sec-intro.tex
missed this one
Removed some old coloring in a few more places.

While traditional models of innovation study lab-based R\&D, we consider data-driven innovation, which crucially depends on data generated by the firm's customers.
We focus on innovation in \emph{exploration technology} which systematically improves the firm's products, whereas prior work would define innovation as improvement in the products themselves. We recover the traditional inverted-U relationship purely through the reputational consequences of exploration.
\asdelete{rather than monetary costs/benefits thereof.}
By contrast, the inverted-U relationships from prior work rely on the monetary aspects: \asedit{investments into  R\&D and profits from innovation.}

>>>>

While traditional models of innovation study lab-based R\&D, we consider data-driven innovation, which crucially depends on data generated by the firm's customers.
We focus on innovation in \emph{exploration technology} which systematically improves the firm's products, whereas prior work would define innovation as improvement in the products themselves. We recover the inverted-U relationship purely through the reputational consequences of exploration.
%\asdelete{rather than monetary costs/benefits thereof.}
By contrast, the inverted-U relationships from prior work rely on the monetary aspects: investments into  R\&D and profits from innovation.
